Create Figures and Tables

### 2023-11-03 Codes/2_figures_tables.rmd
minor error fix

```{r, eval = FALSE}
all_counties <-
  tigris::counties() %>%
  st_simplify(dTolerance = 100) %>%
  rename(
    state_code = STATEFP,
    county_code = COUNTYFP,
    county_name = NAME
  ) %>%
  left_join(., fips_codes, by = c("state_code", "county_code")) %>%
  dplyr::select(state_code, state, county_code, county_name) %>%
  mutate(sc_code = paste0(state_code, county_code)) %>%
  data.table()

>>>>

```{r, eval = FALSE}
#--- fips code ---#
data(fips_codes, package = "tidycensus")

all_counties <-
  tigris::counties() %>%
  st_simplify(dTolerance = 100) %>%
  rename(
    state_code = STATEFP,
    county_code = COUNTYFP,
    county_name = NAME
  ) %>%
  left_join(., fips_codes, by = c("state_code", "county_code")) %>%
  dplyr::select(state_code, state, county_code, county_name) %>%
  mutate(sc_code = paste0(state_code, county_code)) %>%
  data.table()
